---
title: "Lab 02 - Plastic waste"
author: "Lindley Slipetz"
date: "02/3/2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE, warning = FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1


```{r plastic-per-cap, warning = FALSE}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)
```

```{r filter_cap}
plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)
```

```{r continent, warning = FALSE}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) +
  facet_wrap(~continent)
```

Generally, there are similar trends across continents: most countries are clusted under 1. The only outlier is Trinidad and Tobago.

### Exercise 2

```{r plastic-waste-density, fig.width=10,fig.height=11}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.2) +
  scale_fill_viridis_d()
```



The color and fill of the curves were mapped to aesthetics because they are variable dependent. The alpha level applies to all data (not by variable), so it is defined in the plotting geom.

### Exercise 3

```{r box-plot, warning = FALSE}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_boxplot()
```

```{r violin, warning = FALSE}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()
```


The violin plots reveal the shape of the distributions, while the box plots do not. The outliers for continents other than North America are more apparent in the box plots than the violin plots.



### Exercise 4
```{r scatter, warning = FALSE}
ggplot(data = plastic_waste, 
       mapping = aes(x =       
                 mismanaged_plastic_waste_per_cap,
                     y = plastic_waste_per_cap)) +
  geom_point() +
  labs(title = "Mismanaged plastic waste per capita vs plastic waste per capita",
       x = "Mismanaged plastic waste per capita",
       y = "Plastic waste per capita")
```

Most of the countries are grouped towards the origin of the graph. There seems to be a slight positive linear relationship. 


### Exercise 5

color the points in the scatterplot by continent. Does there seem to be any clear distinctions between continents with respect to how plastic waste per capita and mismanaged plastic waste per capita are associated?

```{r scatter-cont, warning = FALSE}
ggplot(data = plastic_waste, 
       mapping = aes(x =       
                 mismanaged_plastic_waste_per_cap,
                     y = plastic_waste_per_cap,
                 color = continent)) +
  geom_point() +
  labs(title = "Mismanaged plastic waste per capita vs plastic waste per capita",
       x = "Mismanaged plastic waste per capita",
       y = "Plastic waste per capita")
```

North America seems to have points with higher plastic waste per capita; though, for most, they are low in mismanaged plastic waste per capita (like the other continents). Africa seems to do the best job of mismanaged plastic waste per capita as the maximum of the its values on the x axis is lower than the other continents. Asia has the worst mismanaged plastic waste per capita. 

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
